### 2012-02-08 paper.tex
A quick proof-read of the paper

\section{Experimental Methods}
\subsection{Reactor setup}
The experiments were performed in silicon-based $\mu$-reactors \cite{Henriksen2009}. The reactor consists of two inlets, a long mixing zone for the reaction gases to allow for diffusional mixing, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide capillary used for probing the gases from the reactor volume. The reactor is sealed by anodic bonding of a pyrex lid to the silicon reactor and is able to operate at a pressure range of 0-2.5\,bar. The reaction gases is supplied through flow controllers capable of controlling flow in the range of 0-10 mL/min. The capillary flow is fed into a quadropole mass-spectrometer for analysis while any surplus of gas from the inlets are passed directly through to the outlet via a pressure controller to control the reactor pressure. The design ensures that all gases exposed to the catalyst under investigation is measured by the mass spectrometer ensuring an extremely high sensitivity of the system.

Before any measurements are performed the reactor is pumped by a turbopump minimizing contaminants in the system. When an evacuated reactor is mounted the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and in operating at $1\,$bar in the reactor the pressure is $\sim5\times10^{-7}\,$mbar in the mass spectrometer chamber.

The reactor is heated by joule heating of a platinum strip evaporated on the backside of the reactor volume. The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the platinum strip using it as a RTD for temperature measurement of the reactor volume. An external thermocouple acts as room-temperature calibration of the RTD as well as sanity check of the RTD measurement during operation.

@@

\subsection{Platinum nanoparticle deposition}
Platinum nanoparticles were deposited from a size-selected cluster source (REF!). Clusters are produced by impinging argon ions on a metal target and condensing these in a cold gas. The cluster are subsequently size-selected by a quadropole mass selection filter. Typical sizes are 3-9\,nm and the coverage is kept at approximately 0.1\% geometric coverage determined by measuring the current on the reactor. After deposition the reactor is anodicly cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid sintering of the nanoparticles.

BEMAERK! Denne tekst er nakket fra et tidligere paper (Carbon,2011). Pre-formed mass-selected platinum particles were soft-landed onto the reactor at room temperature using an inert gas-aggregation source (Mantis Deposition Ltd., Nanogen 50).
The particles are formed by gas-phase condensation from a flux of platinum atoms that are sputtered from a 99.99\% pure Ru target using a magnetron sputter source. The magnetron is housed in a liquid nitrogen cooled enclosure with a 3\,mm diameter aperture at one end. Argon gas is flown into the volume around the magnetron at a rate of 10-120 sccm and is pumped away via the aperture so that a local pressure of 0.1-1 mbar  is obtained inside the gas-aggregation zone during operation. The cooled argon gas thermalises the sputtered platinum atoms so that they condense into clusters, which further coalesce to form nanoparticles. The size of the nanoparticles is determined by a number of factors such as magnetron sputter power (typically 20–40 W), rate of gas flow, distance between the target and the exit aperture and the diameter of the exit aperture. Platinum nanoparticles with diameters in the range of 2–16 nm can be produced using the source \cite{Nielsen2010,Nielsen2009}. The nanoparticles are carried by the gas stream through the exit aperture of the aggregation zone, producing a nanoparticle beam that is further refined by a skimmer. The nanoparticle beam is then passed through a quadrupole mass filter where the ionised fraction (60-80\%) of the nanoparticles can be filtered according to their mass-to-charge ratio.

\section{Results}
An oscillation measurement is performed by mounting a sample in the setup directly after cluster deposition and anodic bonding. Initially a light-off CO-oxidation measurement is performed where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$. At O$_2$:CO ratio of $\sim13$ and a geometrical Pt-coverage of $\sim0.1\%$ lightoff occurs at approximately 180\,$^\circ$C. The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating. After the initial lightoff the sample is cooled to room temperature. When at low temperature the temperature is again increased at 3\,$^\circ$C/min until sustained oscillations occur. A typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical lightoff ramp and the subsequent increase in temperature to achieve sustained oscillations is seen. Often the sample will show oscillations either directly upon lightoff or on the falling temperature ramp.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{initial_treatment.png}
  \caption{A typical example of the initial treatment of a new sample. After performing a lightoff ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place.}
  \label{fgr:initial_treatment}
\end{figure}
The quantitative same behavior has been reproduced on a large number of samples where oscillations also occur. Generally the oscillations have been seen on samples in a wide coverage and particle size regime, however, a geometrical nanoparticle coverage of 0.1\% gave the most consistent oscillations with other samples being less stable with time.

The oscillations are quantitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s.) up to more than an hour. An example of a slow oscillation is seen in Figure~\ref{fgr:full_oscillation}. After a short on-cycle where all CO is converted to CO$_2$ the reaction shows a fast deactivation. After the deactivation the sample quickly regains $\sim$30\% conversion. Hereafter the conversion increases linearly with time until approximately 50\% conversion is reached. Shortly after reaching 50\% conversion the sample again ignites and covert all CO to CO$_2$. After a short full conversion period the sample again deactivates and the cycle repeats itself.
\begin{figure*}
  \centering
  \includegraphics[width=17cm]{single_full_oscillation.png}
  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate de-activation of the sample. For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself.}
  \label{fgr:full_oscillation}
\end{figure*}
Due to flexibility of the setup the pressure in the reactor volume was also varied to observe any change in behavior of the oscillations. In the pressure range of 0.1\,bar to 1\,bar in the reaction volume no change that could be attributed to the pressure was found. The oscillations does not change frequency nor qualitative behavior significantly from the oscillation shown in Figure \ref{fgr:full_oscillation}. Similarly, only a weak dependence on the CO/O$_2$ pressure was observed. At a CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations were observed. Increasing the CO/O$_2$ to $\sim0.175$ showed a clear oscillations with a clear increase in oscillation amplitude compared to lower CO concentrations as observed by the mass spectrometer data. Generally, a tendency towards slower oscillation periods for higher CO/O$_2$ ratio was observed.

After the initial lightoff experiment the nanoparticles show stable self-sustained oscillation. After prolonged measurements over several days an increase in oscillation period was observed as shown in Figure \ref{fgr:long_measurement}. Initially, the oscillation period is $\sim$2.5 minutes and increases linearly with time until 1500 minutes of total oscillation time. Hereafter the oscillations is more irregular which is evident from Figure~\ref{fgr:long_measurement}. At experiment end the oscillation period is between 45 and 20 minutes.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{summary_of_long_measurement.png}
  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition. The sample went through a total of 439 oscillations in 4 days.}
  \label{fgr:long_measurement}
\end{figure}

@@

\section{Discussion}
The CO/O$_2$ dependence showed oscillations from a ratio of 0.025 to 0.175. Richer CO mixtures than 0.175 did not produce any oscillations in our system. The very oxygen rich mixture needed to provoke oscillations agrees with literature \cite{Singh2010,Hendriksen2005}. The is most likely due to the much higher sticking coefficient of CO on platinum which poisons the nanoparticles during the low reactivity region of the cycle.

@@

Due to long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the system setup which due to its small size has timescales on the order of seconds. It is hence hypothesized that the oscillations is a feature related to the nanoparticles. The particles are maybe oxidized? Subsurface, totally oxidized etc. Digt en smuk historie om dette... 
It has already been shown using STM \cite{Hendriksen2002} and FT-IR \cite{Carlsson2006} as well as theoretical studies \cite{Gong2004} that the activity of Pt towards CO oxidation at high pressures is highly dependent on the oxidation state of the surface.

@@

The oscillation period increases with time and becomes increasingly less stable as shown in Figure \ref{fgr:extracts} is consistent across all measured samples. The large scattter in oscillation period can be attributed to the smaller oscillations in between on/off cycles. Occasionally these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period. A possible explanation of the phenomenon could be sintering or roughening of the clusters. Skriv noget mere her...

>>>>

\section{Experimental Methods}
\subsection{Reactor}
The experiments were performed in silicon-based 20x15 mm $\mu$-reactors \cite{Henriksen2009}. The reactor consists of two inlets, a long mixing zone for the reaction gases to allow for diffusional mixing, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide capillary used for probing the gases from the reactor volume. The reactor is sealed by anodic bonding of a pyrex lid to the silicon reactor and is able to operate at a pressure range of 0-2.5\,bar. The reaction gases is supplied to the two inlets by flow controllers capable of controlling the gas flow from 0-10 mL/min. The capillary flow is fed into a quadropole mass-spectrometer for analysis while any surplus of gas from the inlets are passed directly through to the outlet via a pressure controller allowing control of reactor pressure. The design makes sure that all gases exposed to the catalyst under investigation is measured by the mass spectrometer ensuring an extremely high sensitivity of the system.

Before any measurements are performed the reactor is pumped by a turbopump to minimize contaminants in the system. When an evacuated reactor is mounted the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and in operation at $1\,$bar in the reactor volume the pressure is $\sim5\times10^{-7}\,$mbar in the mass spectrometer chamber.

The reactor is heated by joule heating of a platinum strip evaporated on the backside of the reactor volume. The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the platinum strip using it as a RTD for temperature measurement of the reactor. An external thermocouple acts as room-temperature calibration of the RTD as well as sanity check of the RTD measurement during operation.

@@

\subsection{Platinum nanoparticle deposition}
Platinum nanoparticles were deposited in the reactor using a gas-aggregation source (Mantis Deposition Ltd., Nanogen 50). Platinum clusters were formed by gas-phase condensation of platinum atoms produced by impinging argon ions on a 99.99\,\% platinum target in a magnetron sputter source. After condensation the ionised fraction (60-80\%) of the clusters were size-selected by a quadropole mass selection filter according to their mass-to-charge ratio. Using this setup platinum nanoparticles with diameters in the range of 2–16 nm can be produced \cite{Nielsen2010,Nielsen2009}. The size-selected nanoparticles were after size-selection soft-landed in the reactor volume of the microreactor. The coverage was kept at approximately 0.1\% geometric coverage determined by measuring the current on the reactor during deposition. After deposition the reactors were anodicly cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid sintering of the nanoparticles while bonding.

%BEMAERK! Denne tekst er nakket fra et tidligere paper (Carbon,2011). Pre-formed mass-selected platinum particles were soft-landed onto the reactor at room temperature using an inert gas-aggregation source (Mantis Deposition Ltd., Nanogen 50). The particles are formed by gas-phase condensation from a flux of platinum atoms that are sputtered from a 99.99\% pure Ru target using a magnetron sputter source. The magnetron is housed in a liquid nitrogen cooled enclosure with a 3\,mm diameter aperture at one end. Argon gas is flown into the volume around the magnetron at a rate of 10-120 sccm and is pumped away via the aperture so that a local pressure of 0.1-1 mbar  is obtained inside the gas-aggregation zone during operation. The cooled argon gas thermalises the sputtered platinum atoms so that they condense into clusters, which further coalesce to form nanoparticles. The size of the nanoparticles is determined by a number of factors such as magnetron sputter power (typically 20–40 W), rate of gas flow, distance between the target and the exit aperture and the diameter of the exit aperture. Platinum nanoparticles with diameters in the range of 2–16 nm can be produced using the source \cite{Nielsen2010,Nielsen2009}. The nanoparticles are carried by the gas stream through the exit aperture of the aggregation zone, producing a nanoparticle beam that is further refined by a skimmer. The nanoparticle beam is then passed through a quadrupole mass filter where the ionised fraction (60-80\%) of the nanoparticles can be filtered according to their mass-to-charge ratio.

\section{Results}
An oscillation measurement is performed by mounting a sample in the setup directly after cluster deposition and anodic bonding. Initially a light-off CO-oxidation measurement is performed where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$. At O$_2$:CO ratio of $\sim0.08$ and a geometrical platinum coverage of $\sim0.1\%$ lightoff occurs at approximately 180\,$^\circ$C. The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating ramp. After the initial lightoff the sample is cooled to room temperature. When at room temperature the temperature is again increased at 3\,$^\circ$C/min until sustained oscillations occur. A typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical lightoff ramp and the subsequent increase in temperature to achieve sustained oscillations is seen. Often the sample will show oscillations either directly upon lightoff or on the falling temperature ramp.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{initial_treatment.png}
  \caption{A typical example of the initial treatment of a new sample. After performing a lightoff ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place.}
  \label{fgr:initial_treatment}
\end{figure}
The quantitative same behavior has been reproduced on a large number of samples where oscillations also occur. Generally the oscillations have been seen on samples in a wide coverage and particle size regime, however, a geometrical nanoparticle coverage of 0.1\% gave the most consistent oscillations with other samples being less stable with time.

The oscillations are quantitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s.) up to more than an hour. An example of a slow oscillation is seen in Figure~\ref{fgr:full_oscillation}. After a short on-cycle where all CO is converted to CO$_2$ the reaction shows a fast deactivation. After the deactivation the sample quickly regains $\sim$30\% conversion. Hereafter the conversion increases linearly with time until approximately 50\% conversion is reached. Shortly after reaching 50\% conversion the sample again ignites and covert all CO to CO$_2$. After a short full conversion period the sample again deactivates and the cycle repeats itself.
\begin{figure*}
  \centering
  \includegraphics[width=17cm]{single_full_oscillation.png}
  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate de-activation of the sample. For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself.}
  \label{fgr:full_oscillation}
\end{figure*}

Due to flexibility of the setup the pressure in the reactor volume was also varied to observe any change in behavior of the oscillations as a function of pressure. In the pressure range of 0.1\,bar to 1\,bar in the reaction volume no change that could be attributed to the pressure was found. The oscillations does not change frequency nor qualitative behavior significantly from the oscillation shown in Figure \ref{fgr:full_oscillation}. Similarly, only a weak dependence on the CO/O$_2$ pressure was observed. At a CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations were observed. Increasing the CO/O$_2$ to $\sim0.175$ showed clear oscillations with a significant increase in oscillation amplitude compared to lower CO concentrations. Generally, a tendency towards slower oscillation periods for higher CO/O$_2$ ratio was observed.

After the initial lightoff experiment the nanoparticles show stable self-sustained oscillation. After prolonged measurements over several days an increase in oscillation period was observed as shown in Figure \ref{fgr:long_measurement}. Initially, the oscillation period is $\sim$2.5 minutes and increases linearly with time until 1500 minutes of total oscillation time. Hereafter the oscillations is more irregular which as shown in Figure~\ref{fgr:long_measurement}. At experiment end the oscillation period is between 45 and 20 minutes.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{summary_of_long_measurement.png}
  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition. The sample went through a total of 439 oscillations in 4 days.}
  \label{fgr:long_measurement}
\end{figure}

@@

\section{Discussion}
The CO/O$_2$ dependence showed oscillations from a ratio of 0.025 to 0.175. Richer CO mixtures than 0.175 did not produce any oscillations in our system. CO/O$_2$ ratios lower than 0.175 were needed to provoke oscillations in our system. This ratio agrees well with literature \cite{Singh2010,Hendriksen2005} where oscillations have been observed in oxygen rich CO/O$_2$ mixtures. The low concentration of CO in the inlet gases can be attributed to the much higher sticking coefficient of CO on platinum which poisons the nanoparticle surface during the low reactivity region of the cycle. Once poisoned, an increase in temperature would be necessary to ignite the reaction again.

@@

Due to the long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the system setup which due to its small size has timescales on the order of seconds. It is hence concluded that the oscillations is a feature related to the nanoparticles. The particles are maybe oxidized? Subsurface, totally oxidized etc. Digt en smuk historie om dette... 
It has already been shown using STM \cite{Hendriksen2002} and FT-IR \cite{Carlsson2006} as well as theoretical studies \cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric pressures is highly dependent on the oxidation state of the surface.

@@

The oscillation period increases with time and becomes increasingly less stable as shown in Figure \ref{fgr:extracts}. This phenomena is consistent across all measured samples with approximately the oscillation period evolution with time. The large scattter in oscillation period can be attributed to the smaller oscillations in between on/off cycles. Occasionally these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period. A possible explanation of the phenomenon could be sintering or roughening of the clusters. Skriv noget mere her...
